---
title: "Atlier 4"
author: "Jade Sauger"
date: "13/11/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Option 1

```{r}
nutriage <- read.csv("C:/Users/Dadoune/Downloads/Atelier4-master/Atelier4-master/nutriage.csv")
names(nutriage)
```
```{r}
hist(nutriage$taille)
summary(nutriage$taille)
```
H:taille $\sim N(mu,\sigma)$ leproblème $\Pr(taille < 0) >0$

```{r}
mean(nutriage$taille)
sd(nutriage$taille)
```
calculer $\PR(taille < 0)$ avec $taille \sim N(163.9602,9.003368)

```{r}
pnorm(0,mean(nutriage$taille),sd(nutriage$taille))
```

## Option 2

Soit $taille = e^X$ avec $X \sim N(mu,\sigma).$ ALors $X = ln(taille).$

```{r}
x <- log(nutriage$taille)
hist(x)
summary(x)
Q <- seq(from=0,to=1,by=0.1)
Q
qnorm(Q)
```
qq-plot
```{r}
Z <- (x-mean(x))/sd(x)
n <- length(Z)
n
Normal <- rnorm(n)
qqplot(Normal,Z,xlim=c(-3,3),ylim=c(-3,3))
par(new=T)
plot(Z,Z,type="l",col="red",xlim=c(-3,3),ylim=c(-3,3),xlabel="",ylabel="")
```

## Avec le poid 


```{r}
nutriage <- read.csv("C:/Users/Dadoune/Downloads/Atelier4-master/Atelier4-master/nutriage.csv")
names(nutriage)
```

```{r}
hist(nutriage$poids)
summary(nutriage$poids)
```
```
H:poids $\sim N(mu,\sigma)$ leproblème $\Pr(poids < 0) >0$

```{r}
mean(nutriage$poids)
sd(nutriage$poids)
```
calculer $\PR(poids < 0)$ avec $poids \sim N(163.9602,9.003368)

```{r}
pnorm(0,mean(nutriage$poids),sd(nutriage$poids))
```
## Option 2

Soit $poids = e^X$ avec $X \sim N(mu,\sigma).$ ALors $X = ln(poids).$

```{r}
x <- log(nutriage$poids)
hist(x)
summary(x)
Q <- seq(from=0,to=1,by=0.1)
Q
qnorm(Q)
```


qq-plot
```{r}
Z <- (x-mean(x))/sd(x)
n <- length(Z)
n
Normal <- rnorm(n)
qqplot(Normal,Z)
par(new=T)
plot(Z,Z,type="l",col="red",xlim=c(-3,3),ylim=c(-3,3),xlab="",ylab="")
```

cafe
```{r}
table(nutriage$cafe)
mean(nutriage$cafe)
var(nutriage$cafe)
lambda <- (mean(nutriage$cafe)+var(nutriage$cafe))/2
lambda
simul <- rpois(1000,lambda)
table(simul)
```










